SDS 291: Multiple Regression
===========
## TYPE YOUR NAME -- Fall 2018 -- Prof. Reagan

****

HW 1: Due Thursday, September 13, 2012
----
* Reading: Chapter 0 and sections 1.1, 1.2, and 1.3
* Exercises to hand in: #0.9, #0.15, #0.16.

****

```{r, message=FALSE}
require(mosaic)
```

#### Exercise 0.9

> Write your answers below


#### Exercise 0.15

> Here is the initial R code to get you started on 0.15

```{r}
# make sure you get this URL right!
Survey = read.csv("https://andyreagan.github.io/teaching/2018/09-SDS-291/data/Day1Survey.csv")
summary(Survey)
```

> part a: does resting pulse differ by gender?

```{r}
summary(Survey$Pulse)
Males = subset(Survey, Sex == "M")
Females = subset(Survey, Sex == "F")
summary(Males$Pulse)
summary(Females$Pulse)
densityplot(~ Pulse, data=Survey, groups=Sex)
dotplot(~ Pulse | Sex, data=Survey)

```

> part b:


#### Exercise 0.16

> Do women expect to do more reading than men?

> You might want to read about [Welch's t-test](http://en.wikipedia.org/wiki/Welch%27s_t_test), or more generally about [independent two-sample t-tests](http://en.wikipedia.org/wiki/Student%27s_t-test#Independent_two-sample_t-test).
